To Do List

### 2020-09-28 BMC_Genome_Biology_submission/cover_letter_Genome_Biology.Rmd
added additonal bullet pt under main finding to echo main highlight

---
output:
  word_document:
    reference_docx: /Users/mdozmorov/Documents/Work/presentations/Templates/grant_template/styles.doc/NSF_grant_style.docx
  html_document: default
---

@@

- Transcription factors, spatial relationships (distance within the linear genome) between them and boundaries, random undersampling are the necessary features for accurate boundary predictions.

@@

- Biological properties of predicted domain boundaries include the highest genomic signal of CTCF and other transcription factors, more conservation across cell lines, closer proximity to other genomic signatures.

@@

>>>>

---
output:
  pdf_document: default
  html_document: default
  word_document:
    reference_docx: styles.doc/NSF_grant_style.docx
---

@@

- Transcription factors, spatial relationships (distance within the linear genome) between them and boundaries, random under-sampling are the necessary features for accurate boundary predictions.

@@

- Biological properties of domain boundaries predicted using *preciseTAD* include the highest genomic signal of CTCF and other transcription factors, closer proximity to other genomic signatures, and more conservation across cell lines.

@@

- Across cell-line prediction results in similar boundary location as same cell-line prediction, giving rise to the possibility of predicting boundaries for cell-lines of which Hi-C data is currently unavailable.
